---
title: "Homework 6"
author: "Amin Yakubu"
date: "11/24/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(modelr)
```

### Problem 1

In the code chunk below, I am reading in the dataset and creating a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. I will also remove Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race and then Tulsa, AL – this is a data entry mistake.

I will then modify victim_race to have categories white and non-white, with white as the reference category and make victim_age numeric.

```{r}
homicide_df = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv", col_names = TRUE) %>% 
  mutate(city_state = str_c(city, ",", " ", state),
         solved = if_else(disposition == "Closed by arrest", "resolved", "unresolved"),
         solved = fct_relevel(solved, "unresolved"),
         victim_race = tolower(victim_race),
         colpsd_victim_race = fct_collapse(victim_race, "non-white" = c("asian","black", "hispanic", "other", "unknown")),
         colpsd_victim_race = fct_relevel(colpsd_victim_race, "white"),
         victim_age = as.numeric(victim_age)) %>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")))
```

For the city of Baltimore, MD, I will use glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Subsequently, I will obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.

```{r}
baltimore_df = homicide_df %>% 
  filter(city_state == "Baltimore, MD")

fit_logistic_baltimore = glm(solved ~ victim_age + victim_sex + colpsd_victim_race, data = baltimore_df, family = binomial())

fit_logistic_baltimore %>% broom::tidy() %>% 
  janitor::clean_names() %>% 
  mutate(OR = exp(estimate),
         lower_95_ci = exp(estimate - (1.96 * std_error)),
         upper_95_ci = exp(estimate + (1.96 * std_error))) %>% 
  filter(term == "colpsd_victim_racenon-white") %>% 
  select(OR, lower_95_ci, upper_95_ci) %>% 
  knitr::kable(digits = 3)
```

The odds of solving homicides comparing non-white victimes to white victims, adjusting for sex and age is 0.44 (95% CI: 0.31, 0.62).

Now, I will run `glm` for each of the cities in the dataset, each time extracting the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. 

```{r}
fit_logistic_cities = homicide_df %>% 
  #Selecting only the variables needed
  select(city_state, solved, victim_age, victim_sex, colpsd_victim_race) %>%
  #Making listcolumns to use for the iteration
  group_by(city_state) %>% 
  nest() %>% 
  #Using maps to iterate the glm and tidy functions
  mutate(models = map(.x = data, ~ glm(solved ~ victim_sex + colpsd_victim_race + victim_age, 
                                      family = binomial, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% unnest() %>% 
  filter(term == "colpsd_victim_racenon-white") %>% 
  mutate(OR = exp(estimate),
  # Calculating the 95% confidence intervals
         lower_95_ci = exp(estimate - (1.96*std.error)),
         upper_95_ci = exp(estimate + (1.96*std.error))) %>% 
  select(city_state, OR, lower_95_ci, upper_95_ci) %>% 
  #Organizing cities according to estimated OR. From lowest to highest
  mutate(city_state = reorder(city_state, OR))

```

Creating a plot that shows the estimated ORs and CIs for each city. 

```{r}
ggplot(fit_logistic_cities, aes(x = city_state, y = OR )) + 
  geom_point() + 
  geom_errorbar(aes(ymin = lower_95_ci, ymax = upper_95_ci)) + 
  coord_flip() +
  geom_hline(aes(yintercept = 1.00), linetype = "dashed", color = "blue") + 
  labs(
    x = "OR (95% Confidence interval)",
    y = "City, State"
  )
```

We see that in almost all the cities ( expections, Tampa & Birmingham and Durham) have OR below 1.0. This means that in almost all of the cities, the odds of solving a homicide for non-white is less that white category, adjusting for sex and age. However, it is important to note the confidence intervals - about half include the value of 1, meaning they are not statistically significant. 


### Problem 2

```{r}
children_df = read_csv("./data/birthweight.csv") %>% 
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         mrace = as.factor(mrace),
         malform = as.factor(malform))

#checking to see if there are missing variables in any of the variables for the observations
filter_all(children_df, any_vars(is.na(.)))

sum(is.na(homicide_df))

```

There are no missing obervations for the variables. 

Linear regression maybe appropriate, since the outcome of interest is continuous. 

I am hypothesizing that gestational age in weeks is associated with baby's birthweight. Based on literature, I will adjust for
baby's sex, mom's age, mom's race, mom's weight gain and average number of cigarettes smoked per day during pregnancy.


First, I will take a look at the distribution of the two variables. 

```{r}
ggplot(children_df, aes(x = gaweeks)) + geom_histogram()

ggplot(children_df, aes(x = bwt)) + geom_histogram()

ggplot(children_df, aes(x = gaweeks, y = bwt)) + geom_point() + geom_smooth(method = lm)
```

Gestational age in weeks appear to be slightly left skewed. Baby's birthweight appear to be normally distributed. 

```{r}
my_proposed_fit = lm(bwt ~ gaweeks + babysex + momage + mrace  + wtgain + smoken, data = children_df)

linear_fit %>% 
  broom::tidy() 
```

a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r}
children_df %>% 
  modelr::add_residuals(linear_fit) %>% 
  ggplot(aes(x = gaweeks, y = resid)) + geom_violin()
```

```{r}
children_df %>% 
  modelr::add_predictions(linear_fit) %>% 
  ggplot(aes(x = gaweeks, y = pred)) + geom_violin()
```

#### Comparing two non-nested models

I will use cross validation methods to compare the two models below

```{r}
two_term_fit = lm(bwt ~ blength + gaweeks, data = children_df)

three_term_w_interation_fit = lm(bwt ~ bhead * blength *babysex, data = children_df)
```

Cross validation

```{r}
cv_df =
  crossv_mc(children_df, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble))
```


```{r}
cross_validation = cv_df %>% 
  mutate(two_term_fit = map(train, ~ lm(bwt ~ blength + gaweeks, data = .x)),
         three_term_w_interation_fit = map(train, ~ lm(bwt ~ bhead * blength *babysex, data = .x)),
         my_proposed_fit = map(train, ~ lm(bwt ~ gaweeks + babysex + momage + mrace  + wtgain + smoken, data = .x))) %>% 
  mutate(rmse_two_term_fit = map2_dbl(two_term_fit, test, ~ rmse(model = .x, data = .y)),
         rmse_three_term_w_interation_fit = map2_dbl(three_term_w_interation_fit, test, ~ rmse(model = .x, data = .y)),
         rmse_my_proposed_fit = map2_dbl(my_proposed_fit, test, ~ rmse(model = .x, data = .y)))
  
```

```{r}
cross_validation %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
   mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

```{r}
cross_validation %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  group_by(model) %>% 
  summarize(mean_rmse = mean(rmse))
```
































