---
title: "Homework 6"
author: "Amin Yakubu"
date: "11/24/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In the code chunk below, I am creating a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. I will also remove Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race and then Tulsa, AL – this is a data entry mistake.

I will then modify victim_race to have categories white and non-white, with white as the reference category and make victim_age numeric.

```{r}
library(tidyverse)
```

```{r}
homicide_df = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv", col_names = TRUE) %>% 
  mutate(city_state = str_c(city, ",", " ", state),
         solved = if_else(disposition == "Closed by arrest", "resolved", "unresolved"),
         solved = fct_relevel(solved, "unresolved"),
         victim_race = tolower(victim_race),
         colpsd_victim_race = fct_collapse(victim_race, "non-white" = c("asian","black", "hispanic", "other", "unknown")),
         colpsd_victim_race = fct_relevel(colpsd_victim_race, "white"),
         victim_age = as.numeric(victim_age)) %>% 
  filter(city_state != "Dallas, TX" & city_state != "Phoenix, AZ" & city_state != "Kansas City, Mo" & city_state != "Tulsa, AL") 
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.

```{r}
baltimore_df = homicide_df %>% 
  filter(city_state == "Baltimore, MD")

fit_logistic_baltimore = glm(solved ~ victim_age + victim_sex + colpsd_victim_race, data = baltimore_df, family = binomial())

fit_logistic_baltimore %>% broom::tidy() %>% 
  janitor::clean_names() %>% 
  mutate(OR = exp(estimate),
         lower_95_ci = exp(estimate - (1.96 * std_error)),
         upper_95_ci = exp(estimate + (1.96 * std_error))) %>% 
  filter(term == "colpsd_victim_racenon-white") %>% 
  select(OR, lower_95_ci, upper_95_ci)
```

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and  unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

```{r}

```

